---
title: "Week9"
author: "Arushi Arora"
date: "10/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Introduction

This RMD connects to the New York Times 'Movie Reviews' API, constructs an interface in R to read in the JSON data, and transforms it into an R DataFrame.


```{r warning=FALSE}
if(!require('jsonlite'))install.packages('jsonlite')
if(!require('dplyr'))install.packages('dplyr')
```

### Connect to the 'Movie Reviews' API using token
The following syntax only pulls in data on movies that contain the word 'big' between the decade of 1st Jan 1980 and 1st Jan 1990

```{r warning=FALSE}
movies <- fromJSON("https://api.nytimes.com/svc/movies/v2/reviews/search.json?query=big&opening-date=1980-01-01;1990-01-01&api-key=R3MsITKqKA4qKsCAO3RVj86KS48YoNTJ", flatten = TRUE) %>% data.frame()
```

### Convert to dataframe


```{r warning=FALSE}
movie_filter <- movies %>% select (results.display_title, results.mpaa_rating, results.opening_date) %>% head(20)
(movie_filter)

```

### Filter out the movies that had an "R" rating in the list

```{r warning=FALSE}
movie_filter %>% filter(results.mpaa_rating== "R")
```

### Conclusion
9 out of 16 movies that the API returned with the word 'big' in their title were rated 'R'